Minimizing Time Required For Graduation

### 2010-12-04 paper/paper.tex
moved all paper files to a seperate subdirectory, added new figure data file and added figure to paper in 2.2

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{amstext}
% These packages are all incorporated in the memoir class to one degree or another...

@@

@@

Furthermore, to determine if a given student is eligible to register for
a course offering, we can evaluate the rule for the course, where each clause
takes on the value true if a student has already taken the course, and false if
he or she hasn't. If the rule evaluates to true, then the student is eligible to
take the course; otherwise, the student is not.

@@

We these considerations in mind, we begin to develop our heuristic function. In
order to define our heuristic function, we must first define some auxiliary
functions on course offering.  \begin{itemize} \item Let $TimeFromNow(c, q)$ be
difference in quarters between the current quarter, $q$, and the next quarter
a given course offering, $c$, is offered. As there are four quarters, the range
of this function is $\{0, 1, 2, 3\}$.  \item Let $Quarters(c)$ be the number of
quarters per year a given course, $c$, is offered. As there are four quarters,
the range of this function is $\{0, 1, 2, 3, 4\}$.  \item Let $Dependents(c)$ be
the number of course that either directly or indirectly require a given course,
$c$. In our final draft, we will present a diagram illustrating this value more
clearly.  \end{itemize}

\includegraphics[scale=0.5]{more_prereq_tree}

>>>>

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{epsfig}
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{amstext}
% These packages are all incorporated in the memoir class to one degree or another...

@@

\begin{figure} [ht]
    \begin{center}
        \includegraphics[scale=0.4]{prereq_logic_example}
    \end{center}
    \caption{Evaluation of a rule}
    \label{logic_ex}
\end{figure}

@@

Furthermore, to determine if a given student is eligible to register for
a course offering, we can evaluate the rule for the course, where each clause
takes on the value true if a student has already taken the course, and false if
he or she hasn't. If the rule evaluates to true, then the student is eligible to
take the course; otherwise, the student is note. For example, consider
figure~\ref{logic_ex}, here a student has previously taken courses $MATH126$ and
$MATH300$. Since $MATH126$ and $MATH300$ have been taken, then those literals in
the rule for $MATH327$ evaluate to true and therefore the entire rule is true.
Since the entire rule is true, the student can take $MATH327$ when next
available.

@@

\begin{figure} [ht]
    \begin{center}
        \includegraphics[scale=0.35]{more_prereq_tree}
    \end{center}
    \caption{A Prerequisite DAG}
    \label{prereq}
\end{figure}

We these considerations in mind, we begin to develop our heuristic function. In
order to define our heuristic function, we must first define some auxiliary
functions on course offering.  \begin{itemize} \item Let $TimeFromNow(c, q)$ be
difference in quarters between the current quarter, $q$, and the next quarter
a given course offering, $c$, is offered. As there are four quarters, the range
of this function is $\{0, 1, 2, 3\}$.  \item Let $Quarters(c)$ be the number of
quarters per year a given course, $c$, is offered. As there are four quarters,
the range of this function is $\{0, 1, 2, 3, 4\}$.  \item Let $Dependents(c)$ be
the number of course that either directly or indirectly require a given course,
$c$. In Figure~\ref{prereq}, $Dependents(MATH125)$ = 6 while
$Dependents(MATH307)$ = 1 \end{itemize}
